### 2019-04-24 sections/intuition.tex
rename main file to main
micro-optimise sentence in intuition

% \begin{TASK}
%   let makeBreakfast : Task Drink -> Task Food -> Task Unit =
%     \makeDrink. \makeFood. makeDrink <&> makeFood >>? \<<d, f>>. eat d f
%   let main : Task Unit =
%     makeBreakfast (makeTea <?> makeCoffee) makeEgg
% \end{TASK}

@@

% \begin{TASK}
%   let makeBreakfast : Task Drink -> Task Food -> Task Breakfast =
%     \makeDrink. \makeFood. makeDrink <&> makeFood
%   let main : Task Unit =
%     makeBreakfast (makeTea <?> makeCoffee) makeEgg >>? \breakfast. eat breakfast
% \end{TASK}

@@

There are three ways in which tasks are modular.
First, larger tasks are composed of smaller ones.
Second, tasks are first-class, they can be arguments and results of functions.
Third, tasks can be values of other tasks.
These aspects make it possible for programmers to model custom collaboration patterns.

\Cref{exm:breakfast} demonstrates how tasks can be parameterised by other tasks: \TS{makeBreakfast} is a collaboration pattern that always works the same way, regardless of which food and drink are being prepared.

@@

This example demonstrates external communication and choice.
It is a vending machine that dispenses a biscuit for one coin and a chocolate bar for two coins.
\begin{TASK}
  let vend : Task Snack = enter Int >>? \n. if n == 1 then edit Biscuit
    else if n == 2 then edit ChocolateBar else fail
\end{TASK}
The editor $\Enter \Int$ asks the user to enter an amount of money.
This editor stands for a coin slot in a real machine that freely accepts and returns coins.
There is a continue button that is initially disabled, due to the fact that the left hand side of the step combinator has no value.
When the user has inserted exactly 1 or 2 coins, the continue button becomes enabled.
When the user presses the continue button, the machine dispenses either a biscuit or a chocolate bar, depending on the amount of money.
Snacks are modelled using a custom data type.

@@

Several observations can be made on tasks.
One of those is determining the value of a task.
%NOTE: Should we change the type of Value to Maybe v? Both Johan and Alejandro mention that it is not completely clear to them. --NN
% I don't think that we should use Maybe. We should use the term partial function and bottom. --MKL
% I agree! I made the examples here also concrete instead of introducing the value function. --TS
Not all tasks have a value, the empty editor for instance, which makes value observation partial.
For example, the value of $\Edit 7$ is $7$, but the value of $\Enter \Int$ is $\bot$.

@@

The details of the solution are not important here.
What is important is that the implementation of what is essentially deadlock-free waiting for two semaphores requires a substantial amount of additional synchronisation, together with non-trivial conditional statements.

\TOPHAT allows a simple solution to this problem, using guarded steps.
Steps can be guarded with arbitrary expressions.
The parallel combinator can be used to watch two shared editors at the same time.
Let \TS{match}, \TS{paper}, and \TS{tobacco} be references to Booleans.
The smokers are defined as follows.
% The problem is then specified as follows.
\begin{TASK}
  let continue = \<<x,y>>. if x /\ y then smoke else fail in
  let tobaccoSmoker = (update match <&> update paper) >>? continue in
  let paperSmoker = (update tobacco <&> update match) >>? continue in
  let matchSmoker = (update tobacco <&> update paper) >>? continue in
  tobaccoSmoker <&> paperSmoker <&> matchSmoker
\end{TASK}
When the agent supplies two of the ingredients by setting the respective shares to \TS{True}, only the step of the smoker that waits for those becomes enabled.

>>>>

% \begin{TASK}
%   let mkBrkfst : Task Drink -> Task Food -> Task Unit =
%     \makeDrink. \makeFood. makeDrink <&> makeFood >>? \<<d, f>>. eat d f
%   let main : Task Unit =
%     mkBrkfst (makeTea <?> makeCoffee) makeEgg
% \end{TASK}

@@

% \begin{TASK}
%   let mkBrkfst : Task Drink -> Task Food -> Task Breakfast =
%     \makeDrink. \makeFood. makeDrink <&> makeFood
%   let main : Task Unit =
%     mkBrkfst (makeTea <?> makeCoffee) makeEgg >>? \breakfast. eat breakfast
% \end{TASK}

@@

There are three ways in which tasks are modular.
First, larger tasks are composed of smaller ones.
Second, tasks are first-class, they can be arguments and results of functions.
Third, tasks can be values of other tasks.
These aspects make it possible for programmers to model custom collaboration patterns.
%
\Cref{exm:breakfast} demonstrates how tasks can be parameterised by other tasks: \TS{mkBrkfst} is a collaboration pattern that always works the same way, regardless of which food and drink are being prepared.

@@

This example demonstrates external communication and choice.
It is a vending machine that dispenses a biscuit for one coin and a chocolate bar for two coins.
\begin{TASK}
  let vend : Task Snack = enter Int >>? \n. if n == 1 then edit Biscuit
    else if n == 2 then edit ChocolateBar else fail
\end{TASK}
The editor $\Enter \Int$ asks the user to enter an amount of money.
This editor stands for a coin slot in a real machine that freely accepts and returns coins.
There is a continue button that is initially disabled, due to the fact that the left hand side of the step combinator has no value.
When the user has inserted exactly 1 or 2 coins, the continue button becomes enabled.
When the user presses the continue button, the machine dispenses either a biscuit or a chocolate bar, depending on the amount of money.
Snacks are modelled using a custom type.

@@

Several observations can be made on tasks.
One of those is determining the value of a task.
%NOTE: Should we change the type of Value to Maybe v? Both Johan and Alejandro mention that it is not completely clear to them. --NN
% I don't think that we should use Maybe. We should use the term partial function and bottom. --MKL
% I agree! I made the examples here also concrete instead of introducing the value function. --TS
Not all tasks have a value, the empty editor for instance, which makes value observation partial.
I.e., the value of $\Edit 7$ is $7$, but the value of $\Enter \Int$ is $\bot$.

@@

% The details of the solution are not important here.
What is important is that the implementation of what is essentially deadlock-free waiting for two semaphores requires a substantial amount of additional synchronisation, together with non-trivial conditional statements.
%
\TOPHAT allows a simple solution to this problem, using guarded steps.
Steps can be guarded with arbitrary expressions.
The parallel combinator can be used to watch two shared editors at the same time.
Let \TS{match}, \TS{paper}, and \TS{tobacco} be references to Booleans.
The smokers are defined as follows.
% The problem is then specified as follows.
\begin{TASK}
  let continue = \<<x,y>>. if x /\ y then smoke else fail in
  let tobaccoSmoker = (update match <&> update paper) >>? continue in
  let paperSmoker = (update tobacco <&> update match) >>? continue in
  let matchSmoker = (update tobacco <&> update paper) >>? continue in
  tobaccoSmoker <&> paperSmoker <&> matchSmoker
\end{TASK}
When the agent supplies two of the ingredients by setting the respective shares to \TS{True}, only the step of the smoker that waits for those becomes enabled.
